{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Some introduction stuff

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

	In functional data analysis, the concept of a data set can include not only realizations of scalar random variables but also realizations of random functions. These could be the absorption of the Near-infrared (NIR) spectrum, which will be used for the simulation and application. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of its waves on a sample to analyze the interaction of each other. {\color{green} For more details refer to the appendix SECTION ??!??!}.  This dataset can then be used to perform Functional Linear Regression (FLR) on a scalar response variable. To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
%	 In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI) to where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as follows:

	 \begin{equation}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., n
	 \end{equation}

	 where the $x_{i}$ are realizations of a random function $X(\omega)$, $y_i$ are the corresponding realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference. 
	 %For instance, fluctuation in $x_i(s)$ at a point $s_0$ will not have any effect on $Y_i$ if $\beta(s_0)$ = 0. \\
	 The estimation of $\beta(s)$ is inherently an infinite-dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3. Finally, in Section 4, we test the prediction of FLR in a real-world setting.

>>>>

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	As \cite{kokoszka_introduction_2017} {\color{red}(page ca. 17)} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves .

	In functional data analysis, the concept of a data set includes both realizations of scalar random variables and realizations of random functions. These could be the absorption of the Near-infrared (NIR) spectrum, which will be used in later parts of this paper. NIR-spectroscopy uses the near-infrared region of the electromagnetic spectrum (780nm to 2500nm) to measure the absorption of light at different wavelengths in a sample. \footnote{For more details, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  This dataset can then be used, for example, to predict a scalar response variable. To conduct functional linear regression, we need to consider several new concepts and methods that distinguish it from multivariate linear regression.
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., n
	 \end{equation}

	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference. \\

	 {\color{red} This has to be updated.}
	 In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. We report the results of the Monte-Carlo simulation regarding these three different methods in Section 3. Finally, in Section 4, we test the prediction of FLR in a real-world setting.
